```{r, echo = FALSE, warning = FALSE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 999, digits = 0)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",")
})
```

## Transformative Agreements data set

Open APC set up a dedicated collection of data sets comprising articles published under transformative agreements / offsetting deals such as the Springer Compact pilot agreements (Before June 2019 this collection was known as the [offsetting data set](https://github.com/OpenAPC/openapc-de/tree/master/data/offsetting)).

Unlike in the main data set, there is usually no price information included due to the fact that those type of agreements still operate with lump sums and reading fees. This would therefore lead to a biased picture in terms of individual spending per article, at least before the termination of an agreement and when the actual amount of articles published cannot yet be determined.

However, the collection is relevant in view of the discussion on differentiated article prices. Moreover, it provides insights about the allocation of publications over a publisher's journal portfolio which allows predictions on the popularity of journals among researchers.

In order to better identify open access article shares in otherwise subscription journals, universities and research institutions would greatly appreciate any publishers' efforts to comprehensively include open access license information in the CrossRef meta data scheme. As this information is not yet available, the Open APC aggregations of hybrid and offsetting articles may at least provide some insights in this regard. 

Universities and research institutions globally are invited to contribute their APC expenditure data to our initiative in order to build up a comprehensive data set that allows for extensive analyses and fosters transparency on the evolving APC market.        

## Overview
```{r, echo = FALSE, warning = FALSE}
require(dplyr)
require(ezsummary)
my_apc <- readr::read_csv("transformative_agreements.csv")
```
This dataset contains information on `r nrow(my_apc)` articles, published at `r length(unique(my_apc$institution))` institutions under `r length(unique(my_apc$agreement))` different transformative agreements. The data can also be inspected as a [treemap visualisation](http://treemaps.intact-project.org/apcdata/transformative_agreements).

### Breakdown by agreement

```{r}
my_apc %>% select(agreement, euro) %>% 
    group_by(agreement) %>% 
    summarise(count = n()) %>% 
    arrange(desc(count)) %>%
    knitr::kable(col.names = c("Agreement", "Articles"), align = c("l","r"))
```

### Breakdown by institution

```{r}
my_apc %>% select(institution, euro) %>% 
    group_by(institution) %>% 
    summarise(count = n()) %>% 
    arrange(desc(count)) %>%
    knitr::kable(col.names = c("Institution", "Articles"), align = c("l","r"))
```

